\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}

\name{Aravindh Sivalingam}
\address{Chennai, India \quad | \quad Open to UK Relocation}
\address{(+91) 7339513140 \quad | \quad
\href{mailto:adamaravindh@gmail.com}{adamaravindh@gmail.com} \quad | \quad
\href{https://linkedin.com/in/aravindhsiva}{linkedin.com/in/aravindhsiva}}

\begin{document}

%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL SUMMARY}

Engineering Lead with 5.5+ years of experience delivering scalable, rule-driven enterprise systems and automation platforms. Proven track record in CI/CD modernization, cloud migration, agentic workflow automation, and secure microservice architecture. Strong ownership mindset with demonstrated leadership in driving productivity, reliability, and operational efficiency.

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Software Engineering Lead} \hfill Aug 2025 – Present \\
OPTUM Global Solutions, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Built multi-agent automation workflows using Google ADK to streamline transaction handling and reduce manual processing.
\item Own end-to-end CI/CD pipelines ensuring secure, repeatable, and reliable deployments.
\item Leading migration from on-prem infrastructure to AWS, improving scalability and deployment agility.
\item Implemented secure coding practices and reduced vulnerability backlog through proactive remediation.
\item Mentored engineers and improved onboarding through structured technical documentation.
\end{itemize}

\textbf{Senior Software Engineer} \hfill July 2022 – Aug 2025 \\
OPTUM Global Solutions, Hyderabad
\begin{itemize}
\itemsep -3pt {}
\item Migrated CI/CD pipelines from Jenkins to GitHub Actions improving maintainability and pipeline consistency.
\item Transitioned REST services to GraphQL reducing over-fetching and improving API efficiency.
\item Migrated RedHat Rules Engine to Drools and enhanced transaction automation workflows.
\item Designed and built microservices aligned with scalable, event-driven architecture principles.
\end{itemize}

\textbf{Founding Engineer} \hfill Dec 2021 – July 2022 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Designed rule engine powering product automation workflows.
\item Built modular, API-centric architecture supporting scalable enterprise modules.
\item Led frontend and backend integration using ReactJS and Spring Boot.
\end{itemize}

\textbf{Software Engineer} \hfill June 2019 – Dec 2021 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Developed ERP-integrated enterprise modules using Angular and Spring Reactor.
\item Improved UI performance using lazy loading and GraphQL query optimization.
\item Implemented CI/CD using Jenkins and Git version control.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}

Java, TypeScript, Spring Boot, Spring Reactor, Drools, GraphQL, ReactJS, Angular, AWS, GitHub Actions, Jenkins, HashiCorp Vault, Microservices, CI/CD Automation, Secure Deployment Practices

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

B.E. Computer Science and Engineering \\
CGPA: 8.64 / 10

\end{rSection}

\end{document}
