\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}

\name{Aravindh Sivalingam}
\address{Chennai, India \quad | \quad Open to Canada Relocation}
\address{(+91) 7339513140 \quad | \quad
\href{mailto:adamaravindh@gmail.com}{adamaravindh@gmail.com} \quad | \quad
\href{https://linkedin.com/in/aravindhsiva}{linkedin.com/in/aravindhsiva}}

\begin{document}

%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL SUMMARY}

Engineering Lead with 5.5+ years of experience building scalable, cloud-native enterprise systems. Proven expertise in CI/CD modernization, agentic workflow automation, microservices architecture, and secure deployment practices. Strong track record of driving engineering productivity, cross-functional collaboration, and end-to-end delivery in fast-paced environments.

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Software Engineering Lead} \hfill Aug 2025 – Present \\
OPTUM Global Solutions, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Architected multi-agent automation workflows using Google ADK to streamline transaction handling and reduce manual intervention.
\item Owned end-to-end CI/CD pipelines ensuring secure, repeatable, and auditable deployments across environments.
\item Led migration from on-prem infrastructure to AWS, improving scalability, cost efficiency, and deployment agility.
\item Implemented secure coding practices and reduced vulnerability backlog through proactive remediation.
\item Mentored engineers and improved onboarding through structured technical documentation and knowledge sharing.
\end{itemize}

\textbf{Senior Software Engineer} \hfill July 2022 – Aug 2025 \\
OPTUM Global Solutions, Hyderabad
\begin{itemize}
\itemsep -3pt {}
\item Migrated CI/CD pipelines from Jenkins to GitHub Actions improving maintainability and deployment consistency.
\item Transitioned REST services to GraphQL reducing over-fetching and improving API performance.
\item Migrated RedHat Rules Engine to Drools and enhanced transaction automation workflows.
\item Designed and built scalable microservices aligned with event-driven architecture principles.
\end{itemize}

\textbf{Founding Engineer} \hfill Dec 2021 – July 2022 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Designed rule engine powering product automation workflows for enterprise clients.
\item Built modular, API-centric architecture supporting scalable enterprise modules.
\item Led frontend and backend integration using ReactJS and Spring Boot.
\end{itemize}

\textbf{Software Engineer} \hfill June 2019 – Dec 2021 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Developed ERP-integrated enterprise modules using Angular and Spring Reactor.
\item Improved UI performance using lazy loading and GraphQL query optimization.
\item Implemented CI/CD using Jenkins and Git version control.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}

Java, TypeScript, Spring Boot, Spring Reactor, Drools, GraphQL, ReactJS, Angular, AWS, GitHub Actions, Jenkins, HashiCorp Vault, Microservices, CI/CD Automation, Cloud-Native Architecture

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

B.E. Computer Science and Engineering \\
CGPA: 8.64 / 10

\end{rSection}

\end{document}
