\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}

\name{Aravindh Sivalingam}
\address{Chennai, India \quad | \quad Open to US Relocation}
\address{(+91) 7339513140 \quad | \quad
\href{mailto:adamaravindh@gmail.com}{adamaravindh@gmail.com} \quad | \quad
\href{https://linkedin.com/in/aravindhsiva}{linkedin.com/in/aravindhsiva}}

\begin{document}

%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL SUMMARY}

Engineering Lead with 5.5+ years of experience delivering high-impact, scalable enterprise systems and automation platforms. Expertise in agentic workflow automation, CI/CD modernization, cloud migration, and microservices architecture. Strong ownership mindset with a proven ability to drive engineering velocity, system reliability, and cross-team collaboration.

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Software Engineering Lead} \hfill Aug 2025 – Present \\
OPTUM Global Solutions, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Built multi-agent automation workflows using Google ADK to streamline transaction handling and eliminate manual processing bottlenecks.
\item Own end-to-end CI/CD pipelines ensuring secure, repeatable, and reliable deployments at scale.
\item Leading migration from on-prem infrastructure to AWS, improving scalability, cost optimization, and deployment velocity.
\item Implemented secure coding practices and reduced vulnerability backlog through proactive remediation and automated scanning.
\item Mentored engineers and accelerated onboarding through structured technical documentation and pair programming.
\end{itemize}

\textbf{Senior Software Engineer} \hfill July 2022 – Aug 2025 \\
OPTUM Global Solutions, Hyderabad
\begin{itemize}
\itemsep -3pt {}
\item Migrated CI/CD pipelines from Jenkins to GitHub Actions improving maintainability, speed, and pipeline consistency.
\item Transitioned REST services to GraphQL reducing over-fetching and improving API efficiency by 40\%.
\item Migrated RedHat Rules Engine to Drools and enhanced transaction automation workflows.
\item Designed and built microservices aligned with scalable, event-driven architecture principles.
\end{itemize}

\textbf{Founding Engineer} \hfill Dec 2021 – July 2022 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Designed rule engine powering product automation workflows serving enterprise clients.
\item Built modular, API-centric architecture supporting scalable and extensible enterprise modules.
\item Led full-stack integration using ReactJS and Spring Boot.
\end{itemize}

\textbf{Software Engineer} \hfill June 2019 – Dec 2021 \\
CRATOFLOW, Chennai
\begin{itemize}
\itemsep -3pt {}
\item Developed ERP-integrated enterprise modules using Angular and Spring Reactor.
\item Improved UI performance using lazy loading and GraphQL query optimization.
\item Implemented CI/CD using Jenkins and Git version control.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}

Java, TypeScript, Spring Boot, Spring Reactor, Drools, GraphQL, ReactJS, Angular, AWS, GitHub Actions, Jenkins, HashiCorp Vault, Microservices, CI/CD Automation, Agentic Workflow Automation, Secure Deployment Practices

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

B.E. Computer Science and Engineering \\
CGPA: 8.64 / 10

\end{rSection}

\end{document}
